hormones

### 2019-10-11 analysis/07_hormones.Rmd
new colors

manipchar <- c("early",  "inc_d17", "hatch", "prolong", "extend", "n5")
removechar <- c("inc_d3", "M_inc3",  "inc_d9", "M_inc9","inc_d17", "M_inc17","hatch", "M_n2")
```

@@

  hormones %>% 
    filter(study == "characterization",
           hormone %in% c(myhormone))  %>% 
  ggplot(aes(x = treatment, y = plasma_conc, fill = sex)) +
    geom_boxplot() + 
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          legend.position = "none") +
    scale_fill_manual(values = mycolors) +
    labs(y = myylab, x = NULL) 
}

@@

# model and plot prolactin data
mod_prolactin <-  lm(data = prl.char,  plasma_conc ~ treatment + sex)
grid <- prl.char %>%
  data_grid(treatment, sex) %>%
  add_predictions(mod_prolactin)

f <- ggplot(grid, aes(x = treatment, y = pred, color = sex)) +
  geom_point() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "none",
        legend.title = element_blank()) +
  labs(y = "predicted PRL (ng/mL)", x = NULL) +
  geom_smooth(se = F, aes(x = as.numeric(treatment)))

plot_grid(e,f,  rel_widths = c(0.65,0.35))

plot_grid(d + theme(axis.text.x=element_blank()),
          a + theme(axis.text.x=element_blank()),
          c, b, 
          rel_widths = c(0.65,0.35),
          rel_heights = c(0.45,0.55), ncol = 2)

@@

>>>>

manipchar <- c("early",  "inc_d17", "hatch", "prolong", "extend", "n5")
removechar <- c("inc_d3", "M_inc3",  "inc_d9", "M_inc9","inc_d17", "M_inc17","hatch", "M_n2")

sexcolors <- c("female" = "#F8766D", "male" = "#00BFC4")
charcolors <- c("control" = "#F8766D", "bldg" = "#D39200",
                "lay" =  "#93AA00", "inc_d3" = "#00BA38" ,"inc_d9" = "#00C19F" , "inc_d17" =  "#00B9E3", 
                "hatch" = "#619Cff" , "n5" =  "#DB72Fb", "n9" =  "#FF61C3")

@@

  mycolors <- charcolors

  hormones %>% 
    filter(study == "characterization",
           hormone %in% c(myhormone))  %>% 
  ggplot(aes(x = treatment, y = plasma_conc, fill = treatment)) +
    geom_boxplot() + 
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          legend.position = "none") +
    scale_fill_manual(values = mycolors) +
    labs(y = myylab, x = NULL) + 
    facet_wrap(~sex, nrow = 2, scale = "free_x")
}

@@

cd <- plot_grid(e,c,d, nrow = 1)
ab <- plot_grid(a,b, ncol = 1)

plot_grid(cd, ab, rel_widths = c(0.75, 0.25))
```

@@

  mycolors <- sexcolors
